Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (Coleoptera: Curculionid{\ae}), with notes on their distribution and phylogeny

### 2018-03-15 tex/manuscript.tex
rough draft complete with figs
still need to insert measurements

\usepackage{gensymb}
\usepackage{wasysym}
\usepackage{textgreek}
\usepackage{textcomp}
\usepackage{array}
\usepackage{xtab}
\usepackage{dcolumn}
\usepackage{multirow}
\newcolumntype{m}[1]{D{.}{~}{#1}}
\newcommand{\td}{\textdegree~}
\newcommand{\x}{$\times$~}
\newcommand{\breakfill}{\dotfill\newline\penalty0\hbox{}\nobreak\dotfill}

@@

\section*{Introduction}
	The weevil genus \textit{Minyomerus} Horn, 1876 [JF2015] is currently assigned to the tribe Tanymecini Lacordaire, 1863 [non-focal], subtribe Tanymecina Lacoirdaire, 1863 [non-focal] (Curculionid{\ae} [non-focal]: Entimin{\ae} [non-focal] - higher-level classification in accordance with \citealt{alonso1999} and \citealt{bouchard2011}). 
	A recent phylogenetic revision of the genus recognized a total of 17 described species distributed throughout the desert and plains regions of North America \citep{jansen2015}.

@@

	Following the publication of a monographic revision of \textit{Minyomerus} [JF2015], we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet well circumscribed by the generic delimitation of the genus.
	As such, the addition of these new species \emph{does not} alter the definition of the genus (see Phylogenetic results), and we retain the taxonomic concept previously specified by \citet{jansen2015} when referring to this definition.
	For ease of legibility, especially when discussing differences in clade composition when comparing between this and previous work, we use the notation [JF2015] and [JF2018] to specify taxon concepts sec. Jansen \& Franz, 2015 and sec. Jansen \& Franz, 2018, respectively.
	Specifically, all clades inferred in this work will be designated according to the concept [JF2018], \emph{unless} there is perfect congruence (viz. synapomorphies and clade composition) with a clade previously resolved by \citet{jansen2015}, in which case the identifier [JF2015] will be retained.
	While this is the case for all of the previously described species, and a few select clades, we differentiate the newly inferred clade corresponding to the genus, and including the herein described species, as \textit{Minyomerus} [JF2018].

@@

\section*{Materials and methods}
	In order to maximize the compatibility of the new species accounts with the higher-level generic account of \textit{Minyomerus} [JF2015], the methods used in this manuscript are aligned with those of \citet{jansen2015}.
	Here we provide an updated account of the procedures used to generate the species descriptions, distribution maps, and phylogeny herein.
	Most importantly, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.

	\subsection*{Acquisition of museum specimens} 
		The existing set of \textit{Minyomerus} [JF2015] specimens used in the revision of \citet{jansen2015} was supplemented with material from the following collections, using the codens of \citet{arnett1993}:

@@

	\subsection*{Morphological analysis}
		Our systematic and descriptive approach is complementary to \citet{jansen2015}, which in turn follows \citet{franz2010a, franz2010b, franz2012}.
		Terminology for exterior morphology is in general accordance with \citet{torre1989}.
		Additional morphological terms specific to (entimine [non-focal]) weevils were used as follows:
			\citet{ting1936} and \citet{morimoto2003} for mouthparts;
			\citet{thompson1992} for tibial apices and abdominal segments;
			and \citet{oberprieler2014} and \citet{howden1995} for male and female terminalia.

@@

	\subsection*{Phylogenetic analysis}
		The morphological cladistic analysis includes 26 terminal taxa; with 21 ingroup and 5 outgroup terminals.
		The ingroup terminals were represented by 17 species previously assigned to \textit{Minyomerus} [JF2015] and four newly recognized species.
		In keeping with our previous analysis, we sampled outgroups fairly broadly while remaining focused on North American lineages that are putative close relatives of the ingroup \citep{jansen2015, nixon1993}.

@@

	\subsection*{Species distribution modeling}
		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF2015] (Figs.~\#) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
		Cross-validation was used to leverage all available locality data; however, no models could be created for species with two or fewer documented localities.
		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim \citep{hijmans2005}.
		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of the genus.
		Layerwise assembly of tiles was done using QGIS, Version 2.18.16 `Las Palmas', creating composite maps of six tiles each to use in species distribution modeling \citep{qgis2018}.

		The rasterized predictive probabilities were imported into QGIS, where each file was designated a specific color. 
		Each pixel in the raster was assigned a linearly interpolated saturation of that color, with increasing saturation denoting an increased probability of successful prediction of species presence at that point.
		Pixels with a value below 0.50 were rendered transparent so that the maps only show regions with a greater than 50\% chance of successful prediction.
		The raster files were clipped to remove extraneous predicted regions based on: (1) predictive probability (i.e., removing large areas with only transparent pixels) and (2) geographic extent (accounting for endemicity).
		For example, a species endemic to the Snake River Valley of Idaho does not require a predictive model for bioclimatically similar habitats in the Chihuahuan Desert.
		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\#), along with vector layers of country (white) and state (gray) borders \citep{hijmans2012}.

\section*{Descriptions of new species}
	\subsection*{\textit{Minyomerus ampullaceus} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}

@@

			This species is known only from Carlsbad, New Mexico (USA), from an unspecified locality; the location of the city is shown in Fig.~\#.

@@

	\subsection*{\textit{Minyomerus franko} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}

@@

			It is likely to be found throughout the Chihuahuan Desert and arid regions of south-central M\'{e}xico based on habitat similarity (Fig.~\#).

@@

	\subsection*{\textit{Minyomerus sculptilis} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}

@@

			This species has been found in three localities along the Snake River in Idaho (USA), and is thought to be endemic to the Snake River Plain (Fig.~\#).

@@

	\subsection*{\textit{Minyomerus tylotos} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}

@@

			Habitat models (Figs.~\#) predict that this represents the northeastern extent of its range, indicating a strong likelihood that it is present in other parts of the northern Chihuahuan desert, especially in the state of Chihuahua (M\'{e}xico).

@@

\section*{Checklist of species}
	\begin{tabbing}
		\quad \= \quad \= = \= \kill
		\textit{Minyomerus} Horn, 1876: 17\\
				\> \> = \textit{Elissa} Casey, 1888: 271\\
				\> \> \> (synonymized by Kissinger, 1964: 30)\\
				\> \> = \textit{Pseudelissa} Casey, 1888: 273\\
				\> \> \> (synonymized by Pierce, 1909: 359)\\
				\> \> = \textit{Piscatopus} Sleeper, 1960: 84\\
				\> \> \> (synonymized by Jansen \& Franz, 2015: 12)\\
			\> \textit{microps} (Say, 1831: 9) [redescribed by Jansen \& Franz, 2015: 45]\\
				\> \> = \textit{Minyomerus innocuus} Horn, 1876: 18\\
				\> \> \> [former type of \textit{Minyomerus}, designated by Pierce, 1913: 400]\\
				\> \> \> (synonymized by Jansen \& Franz, 2015: 45)\\
				\> \> = \textit{Thylacites microps} Say, 1831: 9\\
				\> \> \> (transferred to \textit{Minyomerus} on the authority of Buchanan \textit{in litt.}\\
				\> \> \> by Blackwelder and Blackwelder, 1948: 46)\\
				\> \> = \textit{Thylacites microsus} Boheman, 1833: 523\\
				\> \> \> (synonymized by LeConte, 1859: 286)\\
			\> \textit{{\ae}riballux} Jansen \& Franz, 2015: 52\\
			\> \textit{ampullaceus} \textbf{sp. nov.}\\
			\> \textit{bulbifrons} Jansen \& Franz, 2015: 81\\
			\> \textit{caseyi} (Sharp, 1891: 151) [redescribed by Jansen \& Franz, 2015: 66]\\
				\> \> = \textit{Pseudelissa caseyi} Sharp, 1891: 151\\
				\> \> \> (genus synonymized by Pierce, 1909: 359)\\
			\> \textit{conicollis} Green, 1920: 194 [redescribed by Jansen \& Franz, 2015: 33]\\
			\> \textit{constrictus} (Casey, 1888: 272) [redescribed by Jansen \& Franz, 2015: 22]\\
				\> \> = \textit{Elissa constricta} Casey, 1888: 272\\
				\> \> \> (genus synonymized by Kissinger, 1964: 30)\\
			\> \textit{cracens} Jansen \& Franz, 2015: 61\\
			\> \textit{franko} \textbf{sp. nov.}\\
			\> \textit{gravivultus} Jansen \& Franz, 2015: 92\\
			\> \textit{griseus} (Sleeper, 1960: 84) [redescribed by Jansen \& Franz, 2015: 96]\\
				\> \> = \textit{Piscatopus griseus} Sleeper, 1960: 84\\
				\> \> \> (genus synonymized by Jansen \& Franz, 2015: 96)\\
			\> \textit{imberbus} Jansen \& Franz, 2015: 18\\
			\> \textit{languidus} Horn, 1876: 18 [redescribed by Jansen \& Franz, 2015: 40]\\
				\> \> = \textit{Pseudelissa cinerea} Casey, 1888: 274\\
				\> \> \> (synonymized by Pierce, 1909: 359)\\
			\> \textit{laticeps} (Casey, 1888: 272) [redescribed by Jansen \& Franz, 2015: 27]\\
				\> \> = \textit{Elissa laticeps} Casey, 1888: 272\\
				\> \> \> (genus synonymized by Kissinger, 1964: 30)\\
			\> \textit{politus} Jansen \& Franz, 2015: 86\\
			\> \textit{puticulatus} Jansen \& Franz, 2015: 75\\
			\> \textit{reburrus} Jansen \& Franz, 2015: 57\\
			\> \textit{rutellirostris} Jansen \& Franz, 2015: 103\\
			\> \textit{sculptilis} \textbf{sp. nov.}\\
			\> \textit{trisetosus} Jansen \& Franz, 2015: 71\\
			\> \textit{tylotos} \textbf{sp. nov.}\\
	\end{tabbing}

\section*{Identification key}
	\begin{xtabular}{@{}
                p{\dimexpr.1\textwidth-\tabcolsep\relax}
                p{\dimexpr.9\textwidth-\tabcolsep\relax}@{}}

@@

\section*{Phylogenetic results}
	A matrix of 52 characters was assembled for the 26 terminal taxa (Tab. 1).
	These characters are comprised of all 46 characters included in the revision of \textit{Minyomerus} [JF2015], plus an additional 6 characters intended to identify putative sister taxa to the newly described species.
	Parsimony analysis returned a single, most-parsimonious cladogram (henceforth MPT) with a length (L) of 99 steps, a consistency index (CI) of 60 and a retention index (RI) of 80 \citep{farris1989}.
	TNT (Tree Analysis Using New Technology) was used to confirm that the shortest tree had been found \citep{goloboff2008}.
	The most-parsimonious cladogram is shown in Fig.~\#, with relative and absolute Bremer support values (see also \# Methods: Phylogenetic analysis) mapped along the left side of each branch; nodes with bootstrap support above 0.95 are marked with a ``*'' symbol to the right of each node.

	The characters, states, and preferred optimizations are described in this section.
	Characters relating to placement of the herein described taxa are discussed in detail in the Discussion (\#) section, along with changes in species group composition and tree topology from \citet{jansen2015}.
	 For all characters not resolved as unreversed synapomorphies, both the individual consistency (ci) and retention (ri) indices are provided.
	Characters are numbered in accordance with descriptive sequence used in the species accounts.
	A ``–'' symbol indicates inapplicable (character, state), whereas a ``?'' symbol indicates missing information, e.g., due to the unavailability of male specimens or insufficient specimens on hand to permit full dissections.
	Characters 9, 27, 39, 45 - 47, 49, and 51 were mapped onto the preferred phylogeny using ACCTRAN optimization (see \citealt{agnarsson2008}), and the remaining characters had an unambiguous optimization.

	\begin{table}[h!]
  	\begin{center}
    	\caption{\textbf{Taxon/character matrix used for for cladistic analysis}. Includes all species of \textit{Minyomerus} [JF2015], newly designated species, and select outgroup taxa. All multistate characters coded as additive, except for character 33. The symbol ``–'' denotes inapplicable character states, whereas ``?'' denotes missing information (see also text).}
    	\label{tab::table1}
    	\ttfamily
    	\footnotesize
    	\begin{tabular}{m{11.10}|l}
      	\toprule
      	\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Taxon{\textbackslash}Character}}} 
      														& ~~~~0~~~~~1~~~~~1~~~~~2~~~~~2~~~~~3~~~~~3~~~~~4~~~~~4~~~~~5~~~\\
      														& ~~~~5~~~~~0~~~~~5~~~~~0~~~~~5~~~~~0~~~~~5~~~~~0~~~~~5~~~~~0~~~\\
      	\midrule
      	Sitona.californicus       & 00-00~?????~00000~00000~00000~00000~00---~-0---~--???~?????~??\\
      	Pandeleteius.cinereus     & 11000~?????~01000~00001~01000~00100~00000~000-0~00???~?????~??\\
      	Pandeleteinus.subcancer   & 11000~?????~01000~00001~01010~00100~00000~000-0~00???~?????~??\\
				Isodrusus.debilis         & 11000~?????~01000~00001~01011~00100~00000~000-0~00???~?????~??\\
				Isodacrys.buchanani       & 11000~?????~01000~00001~01011~00101~00000~000-0~00???~?????~??\\
				Minyomerus.constrictus    & 21100~00010~02110~01002~00011~11211~00000~00000~00000~01010~00\\
				Minyomerus.laticeps       & 21100~00010~02110~01002~00011~11211~00000~00000~00000~01010~00\\
				Minyomerus.imberbus       & 21100~?????~02010~11002~10011~11211~01001~00000~00???~?????~??\\
				Minyomerus.sculptilis     & 21100~?????~02010~11002~10011~11211~01001~00000~00001~00000~10\\
				Minyomerus.conicollis     & 21100~00000~02010~11002~10011~10211~00001~10000~01000~00000~00\\
				Minyomerus.languidus      & 21000~11100~02010~11002~10011~10211~00001~10000~?????~?????~??\\
				Minyomerus.microps        & 21001~11101~02110~11002~10011~10211~00001~10000~10???~?????~??\\
				Minyomerus.tylotos        & 21001~11101~02110~11002~10011~10211~00001~10000~00???~?????~??\\
				Minyomerus.cracens        & 21000~11101~02020~11112~10011~11211~00001~10001~00000~10010~10\\
				Minyomerus.ampullaceus    & 21000~?????~02020~11??2~10011~11211~00001~11001~00???~?????~??\\
				Minyomerus.{\textnormal{\textit{{\ae}}}}riballux  
																	& 22000~11101~12020~11012~10011~20211~00001~11001~10000~00000~01\\
				Minyomerus.reburrus       & 22000~11101~12020~11112~10011~20211~00001~11021~00???~?????~??\\
				Minyomerus.franko         & 21110~10100~02020~11002~10011~11211~00001~10011~10010~00000~01\\
				Minyomerus.caseyi         & 21110~00101~02020~11112~10011~11211~00001~10101~10010~10010~01\\
				Minyomerus.trisetosus     & 21110~00101~02020~11012~10011~10211~00001~10101~10???~?????~??\\
				Minyomerus.gravivultus    & 21100~11101~02120~11002~10011~10211~00111~10000~??010~00000~11\\
				Minyomerus.griseus        & 21100~10101~02120~01002~10111~11211~00111~10000~00010~01100~10\\
				Minyomerus.rutellirostris & 21100~10101~02120~11002~10111~11211~00111~10000~00010~01100~10\\
				Minyomerus.puticulatus    & 21000~11101~02020~11012~10011~11211~10101~10010~01011~01000~11\\
				Minyomerus.bulbifrons     & 21000~11101~02021~11112~10011~10211~10101~10000~01110~01001~01\\
				Minyomerus.politus        & 21000~?????~02021~11112~10011~10211~10101~10010~01111~01001~11\\
      	\bottomrule
    	\end{tabular}
  	\end{center}
	\end{table}

@@

	\subsection*{Phylogenetic placement of newly described species}
		The clades within \textit{Minyomerus} [JF2018] not addressed in the preceding section are identical in topology and composition to those of \textit{Minyomerus} [JF2015], except for the addition of newly described species.
		Here we describe explicitly the phylogenetic placement of these species, and the characters supporting these newly-inferred relationships.
		We additionally discuss, where possible, similarities in biogeographic extent of each species with putative sister taxa, based on the results of species distribution modeling.

>>>>

\usepackage{gensymb}
\usepackage{wasysym}
\usepackage{textgreek}
\usepackage{textcomp}
\usepackage{array}
\usepackage{xtab}
\usepackage{dcolumn}
\usepackage{multirow}
\usepackage{nameref}
\newcolumntype{m}[1]{D{.}{~}{#1}}
\newcommand{\td}{\textdegree~}
\newcommand{\x}{$\times$~}
\newcommand{\breakfill}{\dotfill\newline\penalty0\hbox{}\nobreak\dotfill}
\makeatletter
\def\ttl@useclass#1#2{%
  \@ifstar
    {\ttl@labelfalse\@dblarg{#1{#2}}}
    {\ttl@labelfalse\@dblarg{#1{#2}}}}
\makeatother
\usepackage[counterclockwise]{rotating}
\graphicspath{{figures/}}
\extrafloats{50}

@@

\section*{Introduction}\label{sec:intro}
	The weevil genus \textit{Minyomerus} Horn, 1876 [JF2015] is currently assigned to the tribe Tanymecini Lacordaire, 1863 [non-focal], subtribe Tanymecina Lacoirdaire, 1863 [non-focal] (Curculionid{\ae} [non-focal]: Entimin{\ae} [non-focal] - higher-level classification in accordance with \citealt{alonso1999} and \citealt{bouchard2011}). 
	A recent phylogenetic revision of the genus recognized a total of 17 described species distributed throughout the desert and plains regions of North America \citep{jansen2015}.

@@

	Following the publication of a monographic revision of \textit{Minyomerus} [JF2015], we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet well circumscribed by the generic delimitation of the genus.
	As such, the addition of these new species \emph{does not} alter the definition of the genus (see \textbf{\nameref{sec:results}}), and we retain the taxonomic concept previously specified by \citet{jansen2015} when referring to this definition.
	For ease of legibility, especially when discussing differences in clade composition when comparing between this and previous work, we use the notation [JF2015] and [JF2018] to specify taxon concepts sec. Jansen \& Franz, 2015 and sec. Jansen \& Franz, 2018, respectively.
	Specifically, all clades inferred in this work will be designated according to the concept [JF2018], \emph{unless} there is perfect congruence (viz. synapomorphies and clade composition) with a clade previously resolved by \citet{jansen2015}, in which case the identifier [JF2015] will be retained.
	While this is the case for all of the previously described species, and a few select clades, we differentiate the newly inferred clade corresponding to the genus, and including the herein described species, as \textit{Minyomerus} [JF2018].

@@

\section*{Materials and Methods}\label{sec:methods} 
	In order to maximize the compatibility of the new species accounts with the higher-level generic account of \textit{Minyomerus} [JF2015], the methods used in this manuscript are aligned with those of \citet{jansen2015}.
	Here we provide an updated account of the procedures used to generate the species descriptions, distribution maps, and phylogeny herein.
	Most importantly, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.

	\subsection*{Acquisition of museum specimens}\label{ssec:museum} 
		The existing set of \textit{Minyomerus} [JF2015] specimens used in the revision of \citet{jansen2015} was supplemented with material from the following collections, using the codens of \citet{arnett1993}:

@@

	\subsection*{Morphological analysis}\label{ssec:morph} 
		Our systematic and descriptive approach is complementary to \citet{jansen2015}, which in turn follows \citet{franz2010a, franz2010b, franz2012}.
		Terminology for exterior morphology is in general accordance with \citet{torre1989}.
		Additional morphological terms specific to (entimine [non-focal]) weevils were used as follows:
			\citet{ting1936} and \citet{morimoto2003} for mouthparts;
			\citet{thompson1992} for tibial apices and abdominal segments;
			and \citet{oberprieler2014} and \citet{howden1995} for male and female terminalia.

@@

	\subsection*{Phylogenetic analysis}\label{ssec:phylo} 
		The morphological cladistic analysis includes 26 terminal taxa; with 21 ingroup and 5 outgroup terminals.
		The ingroup terminals were represented by 17 species previously assigned to \textit{Minyomerus} [JF2015] and four newly recognized species.
		In keeping with our previous analysis, we sampled outgroups fairly broadly while remaining focused on North American lineages that are putative close relatives of the ingroup \citep{jansen2015, nixon1993}.

@@

	\subsection*{Species distribution modeling}\label{ssec:dismo} 
		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF2015] (Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
		Cross-validation was used to leverage all available locality data; however, no models could be created for species with two or fewer documented localities.
		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim \citep{hijmans2005}.
		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of the genus.
		Layerwise assembly of tiles was done using QGIS, Version 2.18.16 `Las Palmas', creating composite maps of six tiles each to use in species distribution modeling \citep{qgis2018}.

		The rasterized predictive probabilities were imported into QGIS, where each file was designated a specific color. 
		Each pixel in the raster was assigned a linearly interpolated saturation of that color, with increasing saturation denoting an increased probability of successful prediction of species presence at that point.
		Pixels with a value below 0.50 were rendered transparent so that the maps only show regions with a greater than 50\% chance of successful prediction.
		The raster files were clipped to remove extraneous predicted regions based on: (1) predictive probability (i.e., removing large areas with only transparent pixels) and (2) geographic extent (accounting for endemicity).
		For example, a species endemic to the Snake River Valley of Idaho does not require a predictive model for bioclimatically similar habitats in the Chihuahuan Desert.
		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\ref{fig:map_amptyl}-\ref{fig:map_sculptilis}), along with vector layers of country (white) and state (gray) borders \citep{hijmans2012}.

\section*{Descriptions of New Species}\label{sec:nsp} 
	\subsection*{\textit{Minyomerus ampullaceus} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}\label{ssec:amp}
		Figures~\ref{fig:ampullaceus_F_dorsal}-\ref{fig:ampullaceus_lamina}

@@

			This species is known only from Carlsbad, New Mexico (USA), from an unspecified locality; the location of the city is shown in Fig.~\ref{fig:map_amptyl}.

@@

	\subsection*{\textit{Minyomerus franko} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}\label{ssec:franko}
		Figures~\ref{fig:franko_F_dorsal}-\ref{fig:franko_aedeagus_lateral}

@@

			It is likely to be found throughout the Chihuahuan Desert and arid regions of south-central M\'{e}xico based on habitat similarity (Fig.~\ref{fig:map_franko}).

@@

	\subsection*{\textit{Minyomerus sculptilis} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}\label{ssec:sculpt}
		Figures~\ref{fig:sculptilis_F_dorsal}-\ref{fig:sculptilis_aedeagus_lateral}

@@

			This species has been found in three localities along the Snake River in Idaho (USA), and is thought to be endemic to the Snake River Plain (Fig.~\ref{fig:map_sculptilis}).

@@

	\subsection*{\textit{Minyomerus tylotos} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}\label{ssec:tylotos}
		Figures~\ref{fig:tylotos_F_dorsal}-\ref{fig:tylotos_lamina}

@@

			Habitat models (Figs.~\ref{fig:map_amptyl}) predict that this represents the northeastern extent of its range, indicating a strong likelihood that it is present in other parts of the northern Chihuahuan desert, especially in the state of Chihuahua (M\'{e}xico).

@@

\section*{Checklist of Species}\label{sec:checklist}
	\begin{tabbing}
		\quad \= \quad \= = \= \kill
		\textit{Minyomerus} Horn, 1876: 17\\
				\> \> = \textit{Elissa} Casey, 1888: 271\\
				\> \> \> (synonymized by Kissinger, 1964: 30)\\
				\> \> = \textit{Pseudelissa} Casey, 1888: 273\\
				\> \> \> (synonymized by Pierce, 1909: 359)\\
				\> \> = \textit{Piscatopus} Sleeper, 1960: 84\\
				\> \> \> (synonymized by Jansen \& Franz, 2015: 12)\\
			\> \textit{microps} (Say, 1831: 9) [redescribed by Jansen \& Franz, 2015: 45]\\
				\> \> = \textit{Minyomerus innocuus} Horn, 1876: 18\\
				\> \> \> [former type of \textit{Minyomerus}, designated by Pierce, 1913: 400]\\
				\> \> \> (synonymized by Jansen \& Franz, 2015: 45)\\
				\> \> = \textit{Thylacites microps} Say, 1831: 9\\
				\> \> \> (transferred to \textit{Minyomerus} on the authority of Buchanan \textit{in litt.}\\
				\> \> \> by Blackwelder and Blackwelder, 1948: 46)\\
				\> \> = \textit{Thylacites microsus} Boheman, 1833: 523\\
				\> \> \> (synonymized by LeConte, 1859: 286)\\
			\> \textit{{\ae}riballux} Jansen \& Franz, 2015: 52\\
			\> \textit{ampullaceus} \textbf{sp. nov.}\\
			\> \textit{bulbifrons} Jansen \& Franz, 2015: 81\\
			\> \textit{caseyi} (Sharp, 1891: 151) [redescribed by Jansen \& Franz, 2015: 66]\\
				\> \> = \textit{Pseudelissa caseyi} Sharp, 1891: 151\\
				\> \> \> (genus synonymized by Pierce, 1909: 359)\\
			\> \textit{conicollis} Green, 1920: 194 [redescribed by Jansen \& Franz, 2015: 33]\\
			\> \textit{constrictus} (Casey, 1888: 272) [redescribed by Jansen \& Franz, 2015: 22]\\
				\> \> = \textit{Elissa constricta} Casey, 1888: 272\\
				\> \> \> (genus synonymized by Kissinger, 1964: 30)\\
			\> \textit{cracens} Jansen \& Franz, 2015: 61\\
			\> \textit{franko} \textbf{sp. nov.}\\
			\> \textit{gravivultus} Jansen \& Franz, 2015: 92\\
			\> \textit{griseus} (Sleeper, 1960: 84) [redescribed by Jansen \& Franz, 2015: 96]\\
				\> \> = \textit{Piscatopus griseus} Sleeper, 1960: 84\\
				\> \> \> (genus synonymized by Jansen \& Franz, 2015: 96)\\
			\> \textit{imberbus} Jansen \& Franz, 2015: 18\\
			\> \textit{languidus} Horn, 1876: 18 [redescribed by Jansen \& Franz, 2015: 40]\\
				\> \> = \textit{Pseudelissa cinerea} Casey, 1888: 274\\
				\> \> \> (synonymized by Pierce, 1909: 359)\\
			\> \textit{laticeps} (Casey, 1888: 272) [redescribed by Jansen \& Franz, 2015: 27]\\
				\> \> = \textit{Elissa laticeps} Casey, 1888: 272\\
				\> \> \> (genus synonymized by Kissinger, 1964: 30)\\
			\> \textit{politus} Jansen \& Franz, 2015: 86\\
			\> \textit{puticulatus} Jansen \& Franz, 2015: 75\\
			\> \textit{reburrus} Jansen \& Franz, 2015: 57\\
			\> \textit{rutellirostris} Jansen \& Franz, 2015: 103\\
			\> \textit{sculptilis} \textbf{sp. nov.}\\
			\> \textit{trisetosus} Jansen \& Franz, 2015: 71\\
			\> \textit{tylotos} \textbf{sp. nov.}\\
	\end{tabbing}

\section*{Identification Key}\label{sec:idkey}
	\begin{xtabular}{@{}
                p{\dimexpr.1\textwidth-\tabcolsep\relax}
                p{\dimexpr.9\textwidth-\tabcolsep\relax}@{}}

@@

\section*{Phylogenetic Results}\label{sec:results}
	A matrix of 52 characters was assembled for the 26 terminal taxa (Tab.~\ref{tab:table1}).
	These characters are comprised of all 46 characters included in the revision of \textit{Minyomerus} [JF2015], plus an additional 6 characters intended to identify putative sister taxa to the newly described species.
	Parsimony analysis returned a single, most-parsimonious cladogram (henceforth MPT) with a length (L) of 99 steps, a consistency index (CI) of 60 and a retention index (RI) of 80 \citep{farris1989}.
	TNT (Tree Analysis Using New Technology) was used to confirm that the shortest tree had been found \citep{goloboff2008}.
	The most-parsimonious cladogram is shown in Fig.~\ref{fig:tree}, with relative and absolute Bremer support values (see also \textbf{\nameref{sec:methods}: \nameref{ssec:phylo}}) mapped along the left side of each branch; nodes with bootstrap support above 0.95 are marked with a ``*'' symbol to the right of each node.

	The characters, states, and preferred optimizations are described in this section.
	Characters relating to placement of the herein described taxa are discussed in detail in the \textbf{\nameref{sec:disc}} section, along with changes in species group composition and tree topology from \citet{jansen2015}.
	 For all characters not resolved as unreversed synapomorphies, both the individual consistency (ci) and retention (ri) indices are provided.
	Characters are numbered in accordance with descriptive sequence used in the species accounts.
	A ``–'' symbol indicates inapplicable (character, state), whereas a ``?'' symbol indicates missing information, e.g., due to the unavailability of male specimens or insufficient specimens on hand to permit full dissections.
	Characters 9, 27, 39, 45 - 47, 49, and 51 were mapped onto the preferred phylogeny using ACCTRAN optimization (see \citealt{agnarsson2008}), and the remaining characters had an unambiguous optimization.

	\begin{table}[h!]
  	\begin{center}
    	\caption{\textbf{Taxon/character matrix used for for cladistic analysis}. Includes all species of \textit{Minyomerus} [JF2015], newly designated species, and select outgroup taxa. All multistate characters coded as additive, except for character 33. The symbol ``–'' denotes inapplicable character states, whereas ``?'' denotes missing information (see also text).}
    	\label{tab:table1}
    	\ttfamily
    	\footnotesize
    	\begin{tabular}{m{11.10}|l}
      	\toprule
      	\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Taxon{\textbackslash}Character}}} 
      														& ~~~~0~~~~~1~~~~~1~~~~~2~~~~~2~~~~~3~~~~~3~~~~~4~~~~~4~~~~~5~~~\\
      														& ~~~~5~~~~~0~~~~~5~~~~~0~~~~~5~~~~~0~~~~~5~~~~~0~~~~~5~~~~~0~~~\\
      	\midrule
      	Sitona.californicus       & 00-00~?????~00000~00000~00000~00000~00---~-0---~--???~?????~??\\
      	Pandeleteius.cinereus     & 11000~?????~01000~00001~01000~00100~00000~000-0~00???~?????~??\\
      	Pandeleteinus.subcancer   & 11000~?????~01000~00001~01010~00100~00000~000-0~00???~?????~??\\
				Isodrusus.debilis         & 11000~?????~01000~00001~01011~00100~00000~000-0~00???~?????~??\\
				Isodacrys.buchanani       & 11000~?????~01000~00001~01011~00101~00000~000-0~00???~?????~??\\
				Minyomerus.constrictus    & 21100~00010~02110~01002~00011~11211~00000~00000~00000~01010~00\\
				Minyomerus.laticeps       & 21100~00010~02110~01002~00011~11211~00000~00000~00000~01010~00\\
				Minyomerus.imberbus       & 21100~?????~02010~11002~10011~11211~01001~00000~00???~?????~??\\
				Minyomerus.sculptilis     & 21100~?????~02010~11002~10011~11211~01001~00000~00001~00000~10\\
				Minyomerus.conicollis     & 21100~00000~02010~11002~10011~10211~00001~10000~01000~00000~00\\
				Minyomerus.languidus      & 21000~11100~02010~11002~10011~10211~00001~10000~?????~?????~??\\
				Minyomerus.microps        & 21001~11101~02110~11002~10011~10211~00001~10000~10???~?????~??\\
				Minyomerus.tylotos        & 21001~11101~02110~11002~10011~10211~00001~10000~00???~?????~??\\
				Minyomerus.cracens        & 21000~11101~02020~11112~10011~11211~00001~10001~00000~10010~10\\
				Minyomerus.ampullaceus    & 21000~?????~02020~11??2~10011~11211~00001~11001~00???~?????~??\\
				Minyomerus.{\textnormal{\textit{{\ae}}}}riballux  
																	& 22000~11101~12020~11012~10011~20211~00001~11001~10000~00000~01\\
				Minyomerus.reburrus       & 22000~11101~12020~11112~10011~20211~00001~11021~00???~?????~??\\
				Minyomerus.franko         & 21110~10100~02020~11002~10011~11211~00001~10011~10010~00000~01\\
				Minyomerus.caseyi         & 21110~00101~02020~11112~10011~11211~00001~10101~10010~10010~01\\
				Minyomerus.trisetosus     & 21110~00101~02020~11012~10011~10211~00001~10101~10???~?????~??\\
				Minyomerus.gravivultus    & 21100~11101~02120~11002~10011~10211~00111~10000~??010~00000~11\\
				Minyomerus.griseus        & 21100~10101~02120~01002~10111~11211~00111~10000~00010~01100~10\\
				Minyomerus.rutellirostris & 21100~10101~02120~11002~10111~11211~00111~10000~00010~01100~10\\
				Minyomerus.puticulatus    & 21000~11101~02020~11012~10011~11211~10101~10010~01011~01000~11\\
				Minyomerus.bulbifrons     & 21000~11101~02021~11112~10011~10211~10101~10000~01110~01001~01\\
				Minyomerus.politus        & 21000~?????~02021~11112~10011~10211~10101~10010~01111~01001~11\\
      	\bottomrule
    	\end{tabular}
  	\end{center}
	\end{table}

@@

	\subsection*{Phylogenetic placement of newly described species}\label{ssec:place}
		The clades within \textit{Minyomerus} [JF2018] not addressed in the preceding section are identical in topology and composition to those of \textit{Minyomerus} [JF2015], except for the addition of newly described species.
		Here we describe explicitly the phylogenetic placement of these species, and the characters supporting these newly-inferred relationships.
		We additionally discuss, where possible, similarities in biogeographic extent of each species with putative sister taxa, based on the results of species distribution modeling (see Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}).
